Statistical analysis of Michaelis constant data from online databases

### 2022-02-01 paper.tex
Update paper

% Created 2022-01-31 Mon 09:59
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{color,soul}
\author{Teddy Groves and Areti Tsigkinopoulou}
\date{\today}
\title{Statistical analysis of Michaelis constant data from online databases}
\hypersetup{
 pdfauthor={Teddy Groves and Areti Tsigkinopoulou},
 pdftitle={Statistical analysis of Michaelis constant data from online databases},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.0.91 (Org mode 9.5.2)}, 
 pdflang={English}}
\makeatletter
\newcommand{\citeprocitem}[2]{\hyper@linkstart{cite}{citeproc_bib_item_#1}#2\hyper@linkend}
\makeatother

@@

\section{Introduction}
\label{sec:org528b2a7}
The choice of appropriate parameters for biological models has been a recurring
issue for computational biologists in the recent years. As computational models
become increasingly prominent in the current research
\citeprocitem{1}{[1]}–\citeprocitem{3}{[3]}
and lead the way to biological breakthroughs, the use of high quality parameter
values is becoming essential. In view of these developments, there have been
various efforts to address this issue by employing different
strategies. Although the most popular approach is the estimation of parameters
through optimization methods
\citeprocitem{4}{[4]}, \citeprocitem{5}{[5]},
ensemble modelling strategies are rapidly gaining ground in the field of systems
biology
\citeprocitem{6}{[6]}–\citeprocitem{9}{[9]}
along with the development of tools to define informative parameter priors
\citeprocitem{10}{[10]}, \citeprocitem{11}{[11]}. At
the same time, machine learning methods have recently been gaining popularity as
a tool for interpreting the large amount of existing biological data
\citeprocitem{12}{[12]}–\citeprocitem{14}{[14]}
and have also been employed for the prediction of parameter values (mostly Km
values) in biological models
\citeprocitem{15}{[15]}–\citeprocitem{17}{[17]}.

@@

\section{State of the art}
\label{sec:org96f3597}
The problem of modelling kinetic parameter data from online databases has
previously been addressed in several studies.

@@

\section{Method}
\label{sec:orged9da89}
\subsection{Data fetching}
\label{sec:orged7a9f2}
We fetched data from the SABIO-RK \citeprocitem{21}{[21]}
and BRENDA \citeprocitem{22}{[22]} databases using their publicly
available APIs. We also fetched a list of all EC numbers from the Expasy
database \citeprocitem{23}{[23]}. In the project repository,
see the script \texttt{fetch\_data.py} and the library file \texttt{fetching.py} for code used
to fetch data and the directory \texttt{data/raw/} for the results.

@@

\subsection{Data processing}
\label{sec:orgc838b21}
We made several significant data processing choices. See the library file
\texttt{data\_preparation.py} for code used to implement these choices.

\subsubsection{Filtering}
\label{sec:orgb184998}
For each dataset and kinetic parameter, we removed all reports which failed to
satisfy any of the following conditions:

@@

\subsubsection{Grouping}
\label{sec:orge612070}
Instead of modelling reports directly, we chose to group together reports with
the same biology and study, treating the median log-scale km as a single
observation. We took this decision because of the presence in both datasets of
different kinds of study. In some cases - presumably when the aim of a study was
to discover the sensitivity of a kinetic parameter to changes in conditions -
many reports with the same enzyme, organism, substrate and study are available,
with a range of different kinetic parameter values and different experimental
conditions recorded in the \texttt{commentary} field. In other cases a study will
report only a single value for one kinetic parameter.

@@

\subsection{Statistical model}
\label{sec:orgec5a53f}
We used a Bayesian hierarchical regression model to describe all data. Since Km
parameters are constrained to be positive, we modelled them on natural
logarithmic scale, using the same approach taken in
\citeprocitem{19}{[19]}. Our model includes a global mean
parameter \(\mu\), hierarchical substrate-specific intercept parameters \(a^{sub}\)
and hierarchical intercept parameters \(a^{enz:sub}\), \(a^{ec4:sub}\) and
\(a^{org:sub}\) specific to interactions of substrate and enzyme, ec4 number and
organism respectively. In addition we used a student-T measurement model with
latent standard deviation and degrees of freedom \(\sigma\) and \(\nu\).

@@

\subsection{Model validation}
\label{sec:org77f9da4}
We used a number of standard methods to test our models' validity, aiming to
follow the method described in \citeprocitem{26}{[26]}. To verify the
computation we used standard MCMC convergence metrics and fit our model to fake
data. To assess model specification we performed graphical prior and posterior
predictive checks and both approximate and exact cross validation, using some
simple test models for comparison.

\subsubsection{Computation}
\label{sec:org9fedc54}
For each MCMC run we used arviz \citeprocitem{27}{[27]} to
calculate the improved \hat{R} statistic following the method in
\citeprocitem{28}{[28]} and to check for
divergent transitions. If the \hat{R} statistic was sufficiently close to 1
(i.e. +/- 0.03) and there were no post-warmup divergent transitions we judged
that the computation was likely to have been successful in the sense that the
draws can be treated as samples from the target distribution.

@@

\subsubsection{Comparison models}
\label{sec:org134ceba}
Ideally we would compare the results of our models with previously published
attempts to model the same data. However this was not practical in our case for
two reasons. First, other results are typically derived from different raw
datasets, and rely on different data filtering and summarising decisions. In
particular, we have not previously seen the problem of whether and how to
aggregate results from the same study addressed in detail. Second, the other
results typically assessed model specification by comparing observed data to
point predictions generated by their models. Applying this procedure to our
models would give an incomplete picture, since a single point cannot adequately
summarise the full posterior predictive distribution. In addition, it would not
align with the priorities of our intended users, namely systems biologists
constructing prior distributions for the purpose of ensemble modelling, who we
imagine care more about the extremes of the distributions than central
estimates.

@@

\subsubsection{Graphical posterior predictive checks}
\label{sec:orge66fcab}
Figure \ref{fig:org45dd8d2} below shows our main model's marginal posterior
predictive 1\%-99\% interval for each observation, alongside the observed
value. Ideally exactly 98\% of observations should be covered, and whether or not
an observation is covered should not be systematically predictable.

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./results/plots/ppc_km_sabio_enz.png}
\caption{\label{fig:org45dd8d2}Marginal posterior predictive distributions for main model fit to SABIO Km data}
\end{figure}

In contrast figure \ref{fig:org80f5a54} are graphical posterior predictive checks for the really simple
and simple models.

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./results/plots/ppc_km_sabio_enz_simple.png}
\caption{\label{fig:org80f5a54}Marginal posterior predictive distributions for simple and really simple models fit to SABIO Km data}
\end{figure}

\subsubsection{Cross validation}
\label{sec:orgb754a9c}
For a quantitative compliment to the graphical posterior predictive checks, we
used cross-validation to assess our models' out-of-sample predictive
performance. For exploratory comparison we calculated each model's approximate
leave-one-out expected log predictive density using the method set out in
\citeprocitem{29}{[29]} and implemented in
\citeprocitem{27}{[27]}. To address cases where diagnostics
suggested that the approximate leave-one-out algorithm was likely to be
unreliable we also carried out exact tenfold cross-validation.

@@

\subsection{Web app}
\label{sec:orgb84573d}
\section{Results}
\label{sec:org2a0d786}
\subsection{Marginal distributions of interesting parameters}
\label{sec:org3eae566}
We begin by looking at the marginal distributions of the model's standard
deviation parameters. Comparing these indicates which effects varied the
most. The comparison in figure \ref{fig:org6d5a538} shows that the most important
hierarchical parameter is the substrate effect, followed by the ec4/substrate
interaction, the enzyme/substrate interaction and finally the organism/substrate
interaction. The three larger taus are all clearly greater than the estimated
measurement error \texttt{sigma}, whereas there is overlap between the marginal
distributions for \texttt{sigma} and \texttt{tau\_org\_sub}.

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./results/plots/sd_posteriors.png}
\caption{\label{fig:org6d5a538}Comparison of hierarchical standard deviation parameters}
\end{figure}

Figure \ref{fig:org39dd938} compares the marginal distributions of km
parameters from our best SABIO-RK and BRENDA models. The marginal posterior
distributions in the BRENDA model tend to be narrower, reflecting the larger
input dataset.

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./results/plots/log_km_comparison.png}
\caption{\label{fig:org39dd938}Comparison of measured and modelled Km parameter distributions in BRENDA and SABIO-RK}
\end{figure}

\subsection{Comparison of estimated Kms with physiological metabolite concentrations}
\label{sec:org4b904a8}
Several sources suggest that the Km parameter for a particular organism,
substrate and enzyme should have the same order of magnitude as the typical
physiological concentration of that substrate. \hl{ANOTHER REFERENCE HERE?} For example
\citeprocitem{19}{[19]} write

@@

In order to test whether this is the case, we obtained data about some
physiological metabolite concentrations and compared these with the
corresponding Km measurements and marginal posterior distributions from our
model. Figure \ref{fig:org0dc3ba8} shows the results.

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./results/plots/hmdb_comparison.png}
\caption{\label{fig:org0dc3ba8}Comparison of model predictions with physiological metabolite concentrations from HMDB}
\end{figure}

From the graph it is clear that the first part of the hypothesis is correct, at
least for the metabolites for which we were able to obtain both physiological
concentrations and Km measurements: both are generally in the same order of
magnitude. However, while enzymes with higher physiological concentrations tend
to have higher Km values, this relationship is fairly weak.

This is reflected in our model's marginal posterior distribution for the
parameter \(\tau^{org:sub}\), which concentrates closer to zero than any of the
other hierarchical standard deviation parameters \hl{CHECK THIS IS TRUE}, as can be
seen in figure \ref{fig:org6d5a538}

\subsection{NADH vs NADPH}
\label{sec:orgd69ea28}

Figure \ref{fig:org9ec833e} shows histograms of measured Km parameters from the SABIO-RK
dataset for NADH and NADPH binding enzymes alongside histograms of our final
model's posterior samples for these parameters. We can see that the measurements
for NADPH tended to be higher, and this difference is also present in the posterior
distributions.

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./results/plots/nadh.png}
\caption{\label{fig:org9ec833e}Comparison of modelled and measured Km parameters for NADH and NADPH}
\end{figure}

\subsection{Cofactor vs substrate}
\label{sec:org96fe3d4}
We tested whether there tended to be a systematic difference between the km of
an enzyme's main substrate and that of a cofactor.

\subsection{Which results to use?}
\label{sec:orgb01d466}

@@

\section{Case studies}
\label{sec:org960a2cc}
\section{Discussion}
\label{sec:orgcfc3d46}
\section{References}
\label{sec:orge89aaa4}

@@

\hypertarget{citeproc_bib_item_29}{[29] A. Vehtari, A. Gelman, and J. Gabry, “Practical Bayesian model evaluation using leave-one-out cross-validation and WAIC,” \textit{Statistics and computing}, vol. 27, no. 5, pp. 1413–1432, Sep. 2017, doi: \href{https://doi.org/10.1007/s11222-016-9696-4}{10.1007/s11222-016-9696-4}.}
\end{document}

>>>>

% Created 2022-02-01 Tue 14:40
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{color,soul}
\author{Teddy Groves and Areti Tsigkinopoulou}
\date{\today}
\title{Statistical analysis of Michaelis constant data from online databases}
\hypersetup{
 pdfauthor={Teddy Groves and Areti Tsigkinopoulou},
 pdftitle={Statistical analysis of Michaelis constant data from online databases},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.0.91 (Org mode 9.5.2)}, 
 pdflang={English}}
\makeatletter
\newcommand{\citeprocitem}[2]{\hyper@linkstart{cite}{citeproc_bib_item_#1}#2\hyper@linkend}
\makeatother

@@

\section{Introduction}
\label{sec:orgfc5797f}
The choice of appropriate parameters for biological models has been a recurring
issue for computational biologists in the recent years. As computational models
become increasingly prominent in the current research
\citeprocitem{1}{[1]}–\citeprocitem{3}{[3]}
and lead the way to biological breakthroughs, the use of high quality parameter
values is becoming essential. In view of these developments, there have been
various efforts to address this issue by employing different
strategies. Although the most popular approach is the estimation of parameters
through optimization methods
\citeprocitem{4}{[4]}, \citeprocitem{5}{[5]},
ensemble modelling strategies are rapidly gaining ground in the field of systems
biology
\citeprocitem{6}{[6]}–\citeprocitem{9}{[9]}
along with the development of tools to define informative parameter priors
\citeprocitem{10}{[10]}, \citeprocitem{11}{[11]}. At
the same time, machine learning methods have recently been gaining popularity as
a tool for interpreting the large amount of existing biological data
\citeprocitem{12}{[12]}–\citeprocitem{14}{[14]}
and have also been employed for the prediction of parameter values (mostly Km
values) in biological models
\citeprocitem{15}{[15]}–\citeprocitem{17}{[17]}.

@@

\section{State of the art}
\label{sec:orgce18d1d}
The problem of modelling kinetic parameter data from online databases has
previously been addressed in several studies.

@@

\section{Method}
\label{sec:org78f5d5e}
\subsection{Data fetching}
\label{sec:org583062f}
We fetched data from the SABIO-RK \citeprocitem{21}{[21]}
and BRENDA \citeprocitem{22}{[22]} databases using their publicly
available APIs. We also fetched a list of all EC numbers from the Expasy
database \citeprocitem{23}{[23]}. In the project repository,
see the script \texttt{fetch\_data.py} and the library file \texttt{fetching.py} for code used
to fetch data and the directory \texttt{data/raw/} for the results.

@@

\subsection{Data processing}
\label{sec:org69cb9df}
We made several significant data processing choices. See the library file
\texttt{data\_preparation.py} for code used to implement these choices.

\subsubsection{Filtering}
\label{sec:org044ce9e}
For each dataset and kinetic parameter, we removed all reports which failed to
satisfy any of the following conditions:

@@

\subsubsection{Grouping}
\label{sec:orga4cb87c}
Instead of modelling reports directly, we chose to group together reports with
the same biology and study, treating the median log-scale km as a single
observation. We took this decision because of the presence in both datasets of
different kinds of study. In some cases - presumably when the aim of a study was
to discover the sensitivity of a kinetic parameter to changes in conditions -
many reports with the same enzyme, organism, substrate and study are available,
with a range of different kinetic parameter values and different experimental
conditions recorded in the \texttt{commentary} field. In other cases a study will
report only a single value for one kinetic parameter.

@@

\subsection{Statistical model}
\label{sec:org9456160}
We used a Bayesian hierarchical regression model to describe all data. Since Km
parameters are constrained to be positive, we modelled them on natural
logarithmic scale, using the same approach taken in
\citeprocitem{19}{[19]}. Our model includes a global mean
parameter \(\mu\), hierarchical substrate-specific intercept parameters \(a^{sub}\)
and hierarchical intercept parameters \(a^{enz:sub}\), \(a^{ec4:sub}\) and
\(a^{org:sub}\) specific to interactions of substrate and enzyme, ec4 number and
organism respectively. In addition we used a student-T measurement model with
latent standard deviation and degrees of freedom \(\sigma\) and \(\nu\).

@@

\subsection{Model validation}
\label{sec:org95e5ff9}
We used a number of standard methods to test our models' validity, aiming to
follow the method described in \citeprocitem{26}{[26]}. To verify the
computation we used standard MCMC convergence metrics and fit our model to fake
data. To assess model specification we performed graphical prior and posterior
predictive checks and both approximate and exact cross validation, using some
simple test models for comparison.

\subsubsection{Computation}
\label{sec:orga5a8cb0}
For each MCMC run we used arviz \citeprocitem{27}{[27]} to
calculate the improved \hat{R} statistic following the method in
\citeprocitem{28}{[28]} and to check for
divergent transitions. If the \hat{R} statistic was sufficiently close to 1
(i.e. +/- 0.03) and there were no post-warmup divergent transitions we judged
that the computation was likely to have been successful in the sense that the
draws can be treated as samples from the target distribution.

@@

\subsubsection{Comparison models}
\label{sec:org02fdbca}
Ideally we would compare the results of our models with previously published
attempts to model the same data. However this was not practical in our case for
two reasons. First, other results are typically derived from different raw
datasets, and rely on different data filtering and summarising decisions. In
particular, we have not previously seen the problem of whether and how to
aggregate results from the same study addressed in detail. Second, the other
results typically assessed model specification by comparing observed data to
point predictions generated by their models. Applying this procedure to our
models would give an incomplete picture, since a single point cannot adequately
summarise the full posterior predictive distribution. In addition, it would not
align with the priorities of our intended users, namely systems biologists
constructing prior distributions for the purpose of ensemble modelling, who we
imagine care more about the extremes of the distributions than central
estimates.

@@

\subsubsection{Graphical posterior predictive checks}
\label{sec:org65e677b}
Figure \ref{fig:org9d62348} below shows our main model's marginal posterior
predictive 1\%-99\% interval for each observation, alongside the observed
value. Ideally exactly 98\% of observations should be covered, and whether or not
an observation is covered should not be systematically predictable.

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./results/plots/ppc_sabio-km-enz.png}
\caption{\label{fig:org9d62348}Marginal posterior predictive distributions for main model fit to SABIO Km data}
\end{figure}

Figures \ref{fig:org9e0149b} and \ref{fig:org387aabb} show
graphical posterior predictive checks for the really simple and simple models
fit to the same dataset.

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./results/plots/ppc_sabio-km-simple.png}
\caption{\label{fig:org9e0149b}Marginal posterior predictive distributions for simple model fit to SABIO Km data}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./results/plots/ppc_sabio-km-really-simple.png}
\caption{\label{fig:org387aabb}Marginal posterior predictive distributions for really simple model fit to SABIO Km data}
\end{figure}

From the continuous line of black dots in figure \ref{fig:org9e0149b} we can
see that the posterior predictive intervals have approximately the same order as
the observed data, suggesting that the model is likely overfitting, or at least
not using any structural information from the data.

In contrast figure \ref{fig:org387aabb} shows that the really simple
model is clearly underfitting the observed data - there is no relationship
between the order of the black dots and the blue lines.

\subsubsection{{\bfseries\sffamily TODO} Cross validation}
\label{sec:org57d7028}
For a quantitative compliment to the graphical posterior predictive checks, we
used cross-validation to assess our models' out-of-sample predictive
performance. For exploratory comparison we calculated each model's approximate
leave-one-out expected log predictive density using the method set out in
\citeprocitem{29}{[29]} and implemented in
\citeprocitem{27}{[27]}. To address cases where diagnostics
suggested that the approximate leave-one-out algorithm was likely to be
unreliable we also carried out exact tenfold cross-validation.

@@

\hl{RESULTS OF CROSS VALIDATION COMPARISON}

\subsection{{\bfseries\sffamily DONE} Web app}
\label{sec:orga4f63ea}
In order to make our results accessible to the systems biology community, we wrote a web app that presents them in an easy to use and actionable format. This can be found at \hl{URL}.

The user can choose a dataset, organism, substrate and enzyme and is then
presented with a KDE summary of the corresponding marginal posterior
distribution and some summary statistics describing it, which can be used to
inform a choice of priors.

For each biological category there is an option to choose "Unknown" - in this
case the relevant marginal posterior is calculated dynamically.

The app also provides links from which tables summarising all the marginal
posteriors can be downloaded.

The app was written using Streamlit \citeprocitem{30}{[30]}.

\section{Results}
\label{sec:org7b65808}
\subsection{Marginal distributions of interesting parameters}
\label{sec:org5a237e8}
We begin by looking at the marginal distributions of the model's standard
deviation parameters. Comparing these indicates which effects varied the
most. The comparison in figure \ref{fig:org9d781a4} shows that the most important
hierarchical parameter is the substrate effect, followed by the ec4/substrate
interaction, the enzyme/substrate interaction and finally the organism/substrate
interaction. All of the distributions tend to be greater than that of the
estimated measurement error \texttt{sigma}, suggesting that our model is able to
distinguish all the effects from measurement noise. The substrate and
ec4:substrate taus tend to be the greatest, suggesting that these are the most important predictors.

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./results/plots/sd_posteriors.png}
\caption{\label{fig:org9d781a4}Comparison of hierarchical standard deviation parameters}
\end{figure}

Figure \ref{fig:org42ddc1d} compares the marginal distributions of km
parameters from our best SABIO-RK and BRENDA models. The marginal posterior
distributions in the BRENDA model tend to be narrower, reflecting the larger
input dataset.

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./results/plots/log_km_comparison.png}
\caption{\label{fig:org42ddc1d}Comparison of measured and modelled Km parameter distributions in BRENDA and SABIO-RK}
\end{figure}

\hl{What else to put here? Distributions of $\ln$ kms?}
\subsection{Comparison of estimated Kms with physiological metabolite concentrations}
\label{sec:org4c1309c}
Several sources suggest that the Km parameter for a particular organism,
substrate and enzyme should have the same order of magnitude as the typical
physiological concentration of that substrate. \hl{ANOTHER REFERENCE HERE?} For example
\citeprocitem{19}{[19]} write

@@

In order to test whether this is the case, we obtained data about some
physiological metabolite concentrations from SABIO-RK and compared these with
the corresponding Km measurements and marginal posterior distributions from our
model. Figure \ref{fig:org7c195f7} shows the results.

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./results/plots/concentration_comparison.png}
\caption{\label{fig:org7c195f7}Comparison of model predictions with physiological metabolite concentrations from HMDB}
\end{figure}

The graph on the left shows that our data somewhat support the first part of the
hypothesis: the physiological concentrations are distributed similarly to the
posterior Km samples. The graph on the right suggests that \(\ln\) scale Kms tend to be 1-2 \(\ln\) mM lower than their corresponding physiological concentration reports, give or take about 5 \(\ln\) mM. In other words, there is only a fairly weak relationship between a particular Km and its corresonding physiological concentration.

This is reflected in our model's marginal posterior distribution for the
parameter \(\tau^{org:sub}\), which concentrates closer to zero than any of the
other hierarchical standard deviation parameters \hl{CHECK THIS IS TRUE}, as can be
seen in figure \ref{fig:org9d781a4}

\subsection{NADH vs NADPH}
\label{sec:org1ec26e0}

Figure \ref{fig:orga4246f3} shows histograms of measured Km parameters from the SABIO-RK
dataset for NADH and NADPH binding enzymes alongside histograms of our final
model's posterior samples for these parameters. We can see that the measurements
for NADPH tended to be higher, and this difference is also present in the posterior
distributions.

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./results/plots/nadh.png}
\caption{\label{fig:orga4246f3}Comparison of modelled and measured Km parameters for NADH and NADPH}
\end{figure}

\subsection{{\bfseries\sffamily TODO} Cofactor vs substrate}
\label{sec:org7111380}
We tested whether there tended to be a systematic difference between the km of
an enzyme's main substrate and that of a cofactor.

\subsection{Which results to use?}
\label{sec:orgfb8accf}

@@

\section{{\bfseries\sffamily TODO} Case studies}
\label{sec:org093574d}
\section{{\bfseries\sffamily TODO} Discussion}
\label{sec:org745f9fe}
\section{References}
\label{sec:orgf7cebe3}

@@

\hypertarget{citeproc_bib_item_29}{[29] A. Vehtari, A. Gelman, and J. Gabry, “Practical Bayesian model evaluation using leave-one-out cross-validation and WAIC,” \textit{Statistics and computing}, vol. 27, no. 5, pp. 1413–1432, Sep. 2017, doi: \href{https://doi.org/10.1007/s11222-016-9696-4}{10.1007/s11222-016-9696-4}.}

\hypertarget{citeproc_bib_item_30}{[30] “Streamlit The fastest way to build and share data apps.” Accessed: Feb. 01, 2022. [Online]. Available: \url{https://streamlit.io/}}
\end{document}
